\documentclass[a4paper,10.5pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
\usepackage[compact]{titlesec}
%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.93]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.4\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6.5pt}{6.5pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0.3,0.4,0.8}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}
\AtBeginDocument{%                     % this will reduce spaces between parts (above and below) of texts within a (sub)section to 0pt, for example - like between an 'eqnarray' and text
  \setlength\abovedisplayskip{0pt}
  \setlength\belowdisplayskip{0pt}}
%debug page outer frames
%\usepackage{showframe}

%-----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}} 
\Huge{AMIT PANDEY} \\ [6.5pt] 
\textbf{New Delhi, India}\\
\href{https://github.com/AmitPandey31}{\raisebox{-0.05\height}\faGithub\ GitHub/AmitPandey31} \ $*$ \ 
\href{https://www.linkedin.com/in/amit-pandey-9abb52124/}
{\raisebox{-0.05\height}\faLinkedin\ Linkedin/Amit} \ $*$ \ 
\
\href{mailto:ap896612@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ ap896612@gmail.com} \ $*$ \
\href{tel:+91-9643592611}{\raisebox{-0.05\height}\faMobile \ +91-9643592611} \\
\end{tabularx} \
%----------------------------------------------------------------------------------------
%	ABOUT SECTION
%----------------------------------------------------------------------------------------
\section{About me}
Determined and passionate aspiring \textbf{software developer} with a diverse range of interests in various different \textbf{frontend} and \textbf{backend} languages,  \textbf{responsive frameworks}, databases and best code practices. Driven to become a versatile problem-solver, blending expertise from various domains to build impactful digital innovations. 
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      \textbf{Maharaja Agrasen Institute of Technology (GGSIPU)   Delhi, India} & \hfill \textbf{Graduating August, 2024}\\ [3.75pt]
% \textbf{B.Tech in Electrical and Electronics Engineering} 
B.Tech in Electrical and Electronics Engineering & \hfill \textbf{CGPA : 9.3/10.0} \\

  \textbf{Kendriya Vidyalaya No - 3, Delhi, India} & \hfill \textbf \\
Class XII, (PCM + CS) & \hfill \textbf{CGPA : 8.31/10.0} \\
Class X & \hfill \textbf{CGPA : 10.0/10.0}  
  \resumeSubHeadingListEnd
 \
%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
  \section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Portfolio Site } & \hfill \href{https://github.com/AmitPandey31/PortfolioSite}{\raisebox{-0.05\height}\faGithub\ Code} $|$ \href{https://amitpandey-portfolio.netlify.app/}{\raisebox{-0.05\height}\faLink\ Link}\ \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--]Built a personal portfolio website, equipped with a user-friendly interface showcasing a collection of diverse \textbf{projects}, highlighting my skills and passion as a software developer.  Each equipped with detailed \textbf{descriptions}, \textbf{live} demos, and \textbf{GitHub} links for easy access to the codebase.
         \item[--] Tech Stack :  \textbf{React.js, SCSS, HTML, JavaScript, Sanity, Framer Motion }
    \end{itemize}
    \end{minipage}
    }
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{E-Store} & \hfill \href{https://github.com/AmitPandey31/E-Store}{\raisebox{-0.05\height}\faGithub\ Code} $|$ \href{https://e-store-mocha.vercel.app/}{\raisebox{-0.05\height}\faLink\ Link}\ \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] A seamless shopping platform with secure \textbf{card payment} integration, easy "add to cart" functionality, and a user-friendly interface, providing customers with a delightful online shopping experience. The Owner can \textbf{edit} the \textbf{content} of the site easily with the help of Sanity.io
        \item[--] Tech Stack :  \textbf{HTML, CSS, JavaScript, React.js, Next.js, Sanity}
    \end{itemize}
    \end{minipage}
    }
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Social} & \hfill \href{https://github.com/AmitPandey31/Social}{\raisebox{-0.05\height}\faGithub\ Code} $|$ \href{https://mern-socialapp.netlify.app/}{\raisebox{-0.05\height}\faLink\ Link}\ \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Social is a fully responsive Full Stack social media web application, with the security of \textbf{user authentication}, effortless login and registration, and the comfort of a \textbf{dark mode} interface.
        \item[--] Engage with interactive features like liking, commenting, and connecting with friends, all presented in a \textbf{clean} and intuitive UI that elevates your social media experience to new heights.
         \item[--] Tech Stack :  \textbf{React.js, Node.js, Express, MongoDB, HTML, CSS, MUI}
    \end{itemize}
    \end{minipage}
    }
\end{tabularx}
 \\
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
% Skills
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Languages}& \textbf{:}  \normalsize{C/C++, Python, JavsScript, SQL.}\\
\textbf{Frameworks}& \textbf{:} \normalsize{React.js, Express, Node.js, MongoDB, jQuery, Bootstrap.}\\  
\textbf{Tools}& \textbf{:} \normalsize{VS Code, Git/GitHub, CLI, Postman.}\\ 
\textbf{Technical Skills}& \textbf{:} \normalsize{Data Structures and Algorithms, Object Oriented Programming, DBMS.}
\end{tabularx}
%--------------------------------------------------------------------------------------
\section{CourseWork}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
          \item[--] Mastering \textbf{\href{https://udemy-certificate.s3.amazonaws.com/pdf/UC-0f3ebc1a-da1a-42f6-9a64-6d3c787db55c.pdf}{\raisebox{-0.05\height}\ Data Structures and Algorithms}} using C and C++ by Abdul Bari. 
          \item[--] The Complete \textbf{\href{https://udemy-certificate.s3.amazonaws.com/pdf/UC-5f36e9c4-ba32-45f2-b780-dfeb815082b5.pdf}{\raisebox{-0.05\height}\ Web Development Bootcamp}} by Dr.Angela Yu. 
          \item[--] Completed GDSC \textbf{GCCP}(Google Cloud Career Practioners) Program. \hfill \textbf{\href{https://www.cloudskillsboost.google/public_profiles/7779a7be-9b95-41bd-a6e7-ed6db9792010}{\raisebox{-0.05\height}\ Google Cloud Profile}}
          \item[--] Successfully completed an  \textbf{\href{https://github.com/AmitPandey31/PythonCourse}{\raisebox{-0.05\height}\ IIT-Certified Python}} course, endorsed by the \textbf{Gov of India}.
          
    \end{itemize}
    \end{minipage}
}
\end{tabularx} \\
%----------------------------------------------------------------------------------------
\section{Achievements / Profiles}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
         \item[--] Solved Over 450+ problems on\textbf{\href{https://leetcode.com/AmitPandey31/}{\raisebox{-0.05\height}\ LeetCode}}.
          \item[--] Participated in \textbf{Smart India Hackathon}(SIH). Built an AI-Chatbot using Python and NLP. 
          \item[--] Have a rating of 1500+ on\textbf{\href{https://www.codechef.com/users/amitto}{\raisebox{-0.05\height}\ Codechef}}.
          \item[--] Coding Profile\textbf{\href{https://codeforces.com/profile/Amitto}
          {\raisebox{-0.05\height}\ Codeforces}}.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

\end{document}
